---
output: 
  html_document:
    fig_caption: yes
    css: stylesheets/custom_styles.css
    anchor_sections: FALSE
    includes: 
      in_header: "header_manual.html" 
      after_body: "footer.html"
    self_contained: yes
params:
  park: MIMA # 4-letter park code
  from: 2006 # first year of data
  current: 2022 # current year of data
  nutrient: TRUE # T plots nutrients, but should be complete for season
  plottype: bands # plot bands or boxplot for nutrients
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.pos = "h")
```

```{r libs, include = FALSE, results = 'hide'}
##------------------------------------------------------------------------------
## Load data and libraries
##------------------------------------------------------------------------------
library(NCRNWater)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(plotly)
library(htmltools)
library(leaflet)
library(viridis)
library(kableExtra)
library(lubridate)
library(gridExtra) # for grid.arrange in fake_bands
library(ggpubr) # as_ggplot
library(knitr)
# library(gtable) # grabs manual legend from ggplot object
# library(gridExtra) #grid.arrange
# library(ggpubr) # another way to grab ggplot legend
```
```{r import}
netnwd <- importNCRNWater(Dir = "../data",
                          Data = "Water Data.csv",
                          MetaData = "VizMetaData.csv")

# netnwd <- importNCRNWater(Dir = "./data",
#                          Data = "Water Data.csv",
#                          MetaData = "VizMetaData.csv")
```

```{r legend_cust, warning = F, message = F, include = F, echo = F, results = 'hide'}
source("fake_bands_legend_code.R") # creates legend with fake data 
#source("./rmd/fake_bands_legend_code.R") 
```

```{r globvars, message = F, include = F}
##------------------------------------------------------------------------------
## Global variables
##------------------------------------------------------------------------------
# Variables for cat asis code, which can't take params
# parkcode = "MIMA"
# current = 2022
# from = 2006
# to = 2021
# nutrient = TRUE
# plottype = 'bands'
# params <- data.frame(plottype = 'bands')

current = params$current
to = current - 1
parkcode = params$park
from = params$from
nutrient = params$nutrient
plottype = params$plottype

# Determine whether waterboxplot_function needs to be evaluated
boxplot_eval = ifelse(params$plottype != 'bands', TRUE, FALSE)

# Long park name
long_name = getParkInfo(netnwd, park = parkcode, info = "ParkLongName")

# Load water data for given park and add variables needed for plotting
wdata <- getWData(netnwd, parkcode = parkcode, output = 'dataframe')
wdata <- wdata |> mutate(year = year(Date),
                       month = month(Date, label = TRUE, abbr = TRUE),
                       month_num = as.numeric(month))

if(nrow(wdata |> filter(year == current)) == 0){
  stop(paste0("There are no data available for ", parkcode, " in specified year ", current))
}

# List of sites
site_list_all <- sort(unique(wdata$Site))
site_curr <- sort(unique(wdata$Site[wdata$year == current]))

# Set up site_list so only includes sites sampled in current year
site_list <- site_list_all[site_list_all %in% site_curr]

# Create site key for sitecode and type
site_key <- purrr::map_dfr(site_list,
  ~data.frame(Site = getSiteInfo(netnwd, parkcode = parkcode, 
                                sitecode = ., info = "SiteCode"),
             SiteName = getSiteInfo(netnwd, parkcode = parkcode, 
                                    sitecode = ., info = "SiteName"),
             SiteType =  getSiteInfo(netnwd, parkcode = parkcode, 
                                     sitecode = ., info = "type")))

# Import lower and upper assessment values and join with wdat
charinfo <- data.frame(
  Site = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site,
                     info = "SiteCode"),
  CharName = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site, 
                         info = "CharName"),
  DisplayName = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site, 
                         info = "DisplayName"),
  unit = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site,
                     info = "Units"),
  type = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site,
                     info = "type"), 
  param_name = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site,
                           info = "CategoryDisplay"),
  LowerPoint = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site, 
                           info = "LowerPoint"),
  UpperPoint = getCharInfo(netnwd, parkcode = parkcode, sitecode = site_key$Site, 
                           info = "UpperPoint"))

# Combine WQ thresholds with water data
wdata2 <- left_join(wdata, charinfo, by = c("Site", "Characteristic" = "CharName"), 
                  multiple = "all", relationship = 'many-to-many') |> 
          mutate(pcolor = 
           ifelse(!is.na(UpperPoint) & year == current & ValueCen > UpperPoint, 
                  "Poor WQ value",
           ifelse(!is.na(LowerPoint) & year == current & ValueCen < LowerPoint, 
                  "Poor WQ value", "Current value")),
           yname = ifelse(param_name != 'pH', paste0(param_name, " (", unit, ")"), "pH"))

# Add site names to water data
wdata_full <- left_join(wdata2 |> select(-type), site_key, by = "Site") |> arrange(Date)
wdata_curr <- wdata_full |> filter(year == current)
wdata_hist <- wdata_full |> filter(year < current)

# Turn on comp tab if park has more than one site
show_comp <- ifelse(length(site_list) > 1, TRUE, FALSE)
show_comp_n <- ifelse(show_comp == TRUE & nutrient == TRUE, TRUE, FALSE)

```

```{r waterboxplot, eval = boxplot_eval}
source("waterboxplot_function.R")
# source("./rmd/waterboxplot_function.R")
```

```{r site_comp_setup, echo = F, warning = F, message = F, eval = show_comp}
##------------------------------------------------------------------------------
## Physical site comp setup
##------------------------------------------------------------------------------
# List of physical parameters in park
char_list_p <- sort(unique(wdata_full$Characteristic[wdata_full$Category == 'physical']))

char_list_p_comp <- if(parkcode %in% c("MABI", "MIMA")){char_list_p[!(char_list_p %in% "Discharge_cfs")]
  } else {char_list_p}

# Turn off all legends except last in list to remove legend duplicates from subplot
legend_list_p <- c(rep("none", length(char_list_p_comp)-1), "bottom")

# Create list of plots comparing physical parameters across all sites in park
comp_plots_p <- purrr::map2(char_list_p_comp, legend_list_p,
                            ~ggplotly(
                              watersite_comps(netnwd, year = current, 
                                      parkcode = parkcode, 
                                      sitecode = site_list,
                                      charname = .x,
                                      legend = .y) + 
                              labs(color = NULL, fill = NULL, 
                                   shape = NULL, linetype = NULL),
                            tooltip = 'text')) |> 
                set_names(char_list_p_comp)
                #name plots to refer to them by char name

# leg_comp_p <- as_ggplot(get_legend(
#   watersite_comps(netnwd, year = current, parkcode = parkcode,
#                   sitecode = site_list, 
#                   charname = char_list_p[length(char_list_p)],
#                   legend = 'bottom'# take last instead of discharge
#                   )))

# MABI has stream and pond sites in comparison, so have fewer comp plots
hts = if(length(comp_plots_p) <= 4){c(0.5, 0.5)} else {c(0.325, 0.35, 0.325)}
rws = if(length(comp_plots_p) <= 4){2} else {3}
# Use plot list to create matrix of plots (plotly subplot)
comp_plots_p_final <- subplot(comp_plots_p[1:length(comp_plots_p)],
                         titleY = TRUE, titleX = FALSE, margin = 0.08,
                         #create 3 rows if more than 4 plots, otherwise 2 rows
                         nrows = rws,
                         #set height of each row (default makes middle row shorter)
                         heights = hts) |> 
  # turn off subplot legend
  style(showlegend = FALSE) |> 
  # manually set width and height of subplot
  layout(autosize = FALSE)#, width = 900, height = 650)

num_sites <- c(1:length(site_curr))

# Turn on legend elements 
for (i in 1:length(num_sites)){
  comp_plots_p_final$x$data[[i]]$showlegend <- TRUE #site (line/markers)
  comp_plots_p_final$x$data[[length(comp_plots_p_final$x$data)]]$showlegend <- TRUE #threshold line
  comp_plots_p_final$x$data[[length(comp_plots_p_final$x$data)]]$name <- "WQ Threshold" #set name
}

# Move legend down slightly and make it horizontal
comp_plots_p_final <- comp_plots_p_final  |>  layout(legend = list(x = 0, y = -0.15, orientation = "h"))
```

```{r site_comp_setup_n, echo = F, warning = F, message = F, eval = show_comp_n, erro = TRUE}
##------------------------------------------------------------------------------
## Nutrients site comp setup
##------------------------------------------------------------------------------
# List of nutrient parameters to include in site comparison
char_list_n <- c("TN_mgL", "TP_ugL")

# Turn off all legends except last in list to remove legend duplicates from subplot
legend_list_n <- c(rep("none", length(char_list_n)-1), "bottom")

# Create list of plots comparing physical parameters across all sites in park
comp_plots_n <- purrr::map2(char_list_n, legend_list_n,
                         ~watersite_comps(netnwd, 
                                          year = current, 
                                          parkcode = parkcode, 
                                          sitecode = site_list,
                                          charname = .x,
                                          legend = .y)+ 
                              labs(color = NULL, fill = NULL, shape = NULL, linetype = NULL)) |> 
                          #facet_wrap(~Characteristic) |> 
                set_names(char_list_n) #name plots to refer to them by char name

# Use plot list to create matrix of plots (plotly subplot)
comp_plots_n_final <- subplot(comp_plots_n[1:length(comp_plots_n)],
                         titleY = TRUE, titleX = FALSE, margin = 0.08, nrows = 1) |> 
  # turn off subplot legend, manually set height and width of subplot
  style(showlegend = FALSE) |> layout(autosize = FALSE)#, width = 900, height = 300)

num_sites <- c(1:length(site_curr))

# Turn on legend elements 
for (i in 1:length(num_sites)){
  comp_plots_n_final$x$data[[i]]$showlegend <- TRUE #site (line/markers)
  comp_plots_n_final$x$data[[length(comp_plots_n_final$x$data)]]$showlegend <- TRUE #threshold line
  comp_plots_n_final$x$data[[length(comp_plots_n_final$x$data)]]$name <- "WQ Threshold" #set name
}

# Move legend down slightly and make it horizontal
comp_plots_n_final <- comp_plots_n_final |> layout(legend = list(x = 0, y = -0.15, orientation = "h"))
```

# `r long_name` {.tabset .tabset-fade .tabset-pills}

```{r p_site_comp, results = 'asis', include = show_comp}
##------------------------------------------------------------------------------
## Physical site comp plots                            
##------------------------------------------------------------------------------
# Create comparison tab
cat("## ", "All Sites","{.tabset}", "\n")

# Create a physical parameter subtab if also reporting nutrients
if(nutrient == TRUE){cat("### ", "Field Measurements", "\n")}

# Title of tab
cat("<h2>Monthly Water Quality Measurements", paste0("(", parkcode, " ", current, ")"),"</h2>")

# Figure caption 
fig_cap_p <- htmltools::withTags(body(
                          'The plots below compare monthly
                          measurements across all', long_name, 'sites during the',
                          current, 'field season. Only water quality parameters
                          that are measured at multiple sites are included. 
                          Water quality thresholds are derived from state surface 
                          water quality standards. Parameter abbreviations and 
                          additional information are defined in "About the Data".'))

cat(as.character(fig_cap_p))
```

```{r p_site_comp_plots, results = 'show', fig.height = 7.5, eval = show_comp}

comp_plots_p_final

# NOTE: The space directly below between p_site_comp and n_site_comp is necessary 
# for tabset to work in a combined report (physical and nutrients) 
# Adding cat("\n") does not work
```

```{r n_site_comp, results = 'asis', include = show_comp}
##------------------------------------------------------------------------------
## Nutrient site comp plots                            
##------------------------------------------------------------------------------
# Create nutrient subtab if reporting nutrients
if(nutrient == TRUE) {cat("### ", "Lab Chemistry", "\n")}

# Subtab title
if(nutrient == TRUE) {cat("<h2>Monthly Water Quality Measurements", 
                        paste0("(", parkcode, " ", current, ")"),"</h2>")}

# Figure caption
fig_cap_n <- htmltools::withTags(body(
                          'The plots below compare monthly
                          measurements across all', long_name, 'sites during the',
                          current, 'field season. Only water quality parameters
                          that are measured at multiple sites are included. Water 
                          quality thresholds represent the lower 5th percentile 
                          of reference waters in the region, and separate moderate 
                          from most disturbed sites. Parameter 
                          abbreviations and additional information are defined in 
                          "About the Data".'))

if(nutrient == TRUE) {cat(as.character(fig_cap_n))}
```

```{r n_site_comp_plots, results = 'show', fig.height = 4.5, eval = show_comp}
if(nutrient == TRUE) {comp_plots_n_final}
```

```{r site_tab_setup, warning = F, message = F}
##------------------------------------------------------------------------------
## Physical site tab setup                            
##------------------------------------------------------------------------------
# Create dataframe of physical parameters
char_list_p <- unique(wdata_full[wdata_full$Category == "physical" & 
                      wdata_full$Park == parkcode &
                      wdata_full$year == current,
                      c("Site", "Characteristic")]) |> arrange(Site, Characteristic)

plot_list_p <- map2(char_list_p$Site, char_list_p$Characteristic, 
                  ~waterbands(netnwd, parkcode = parkcode, sitecode = .x, 
                              charname = .y, year_current = current,
                              year_historic = from, legend = "none")) |> 
               set_names(char_list_p$Site)
```

```{r site_tab_setup_n, warning = F, message = F, error = T, eval = show_comp_n}
##------------------------------------------------------------------------------
## Nutrient site tab setup                            
##------------------------------------------------------------------------------
# LNETN target nutrients
stream_nutrients <- c("TP_ugL", "TN_mgL", "ANC_ueqL")
lake_nutrients <- c("TP_ugL", "TN_mgL", "ChlA_ugL")

# Create dataframe of nutrient parameters
char_list_n <- unique(wdata_full[wdata_full$Category == "nutrients" & 
                      wdata_full$Park == parkcode &
                      wdata_full$year == current,
                      c("Site", "Characteristic", "SiteType")]) |> arrange(Site, Characteristic)

# Select target nutrients by site
site_char_list_n <- char_list_n |> 
  filter((SiteType == "Lake" & Characteristic %in% lake_nutrients) | 
         (SiteType == "Stream" & Characteristic %in% stream_nutrients))

# Iterate on dataframe to create nutrient plots
# If > 2 months available for 4 years, then use waterbands instead of boxplots
# params = data.frame(plottype = 'bands')
plot_list_n <- 
  if(plottype == "bands"){
    map2(site_char_list_n$Site, site_char_list_n$Characteristic, 
         ~waterbands(netnwd, parkcode = parkcode, sitecode = .x, 
                     charname = .y, year_current = current,
                     year_historic = from, legend = "none")) |> 
         set_names(site_char_list_n$Site)

} else {
    map2(site_char_list_n$Site, site_char_list_n$Characteristic, 
         ~waterboxplot(sitecode=.x, charname=.y)) |> 
         set_names(site_char_list_n$Site)
}

```

```{r site_tabs, warning = F, message = F, results='asis'}
##------------------------------------------------------------------------------
## Site tabs                           
##------------------------------------------------------------------------------
# Loop on list of sites to create tabs for each site and fill them with plots
for(i in seq_along(site_list)){
  
  #site <- site_list[1]
  site <- site_list[i] # change back to i
  site_name <- site_key$SiteName[site_key$Site == site]
  
  num_plots_p <- length(plot_list_p[names(plot_list_p) == site])
  num_plots_n <- ifelse(exists("plot_list_n") & nutrient == TRUE, 
                        length(plot_list_n[names(plot_list_n) == site]), 0)
  
  plot_title <- htmltools::withTags(h2('Historic', paste0('(', from, ' to ', to, ')'),
                  'vs. Current', paste0('(', current,')'), 'Measurements'))
  
  # Physical parameters (waterbands) figure caption                                               
  fig_cap_p <- htmltools::withTags(body('The plots below show historic ranges for', site_name, 
                                        'based on the range of measurements collected from',
                                        from, 'to', to, 'for each month. The outermost band represents the
                                        historic maximum and minimum value collected for each month.
                                        The second inner band represents the 95% range of historic values
                                        by month. The innermost band represents the 50% range of historic
                                        values by month. The points represent the most 
                                        recent measurements collected in', current, 'by month. 
                                        Water quality thresholds are derived from state surface water quality 
                                        standards. Parameter abbreviations and additional information are
                                        defined in "About the Data".'))
  # Nutrient parameters (boxplot) figure caption
  fig_cap_n <- htmltools::withTags(body('The boxplots below show historic ranges for', site_name, 
                                        'based on the range of measurements collected from', from, 'to', to, 
                                        'for each month. The lower and upper box boundaries represent the 
                                        25th (Q1) and 75th (Q3) percentiles, respectively, and together show 
                                        the interquartile range (IQR). The line inside the box is the 50th 
                                        percentile (median). Asterisks outside of the lower and 
                                        upper fence range (Q1 - 1.5*IQR, Q3 + 1.5*IQR) are considered 
                                        outliers. The points represent the most recent 
                                        measurements collected in', current, 'by month. Water 
                                        quality thresholds represent the lower 5th percentile 
                                        of reference waters in the region, and separate moderate 
                                        from most disturbed sites. 
                                        Parameter abbreviations and additional information are defined in
                                        "About the Data".'))
  
  # Fig heights need to be separate params because the tab template doesn't allow duplicates
  fig_height_p <- ifelse(num_plots_p > 4, 6.5, 4.5)
  fig_height_n <- ifelse(num_plots_n > 4, 6.5, 4.5)
  fig_width <- 9.3
  
  # Physical subplot
  subplots_p <- subplot(plot_list_p[names(plot_list_p) == site][1:num_plots_p],
                        titleY = TRUE, titleX = FALSE, #margin = 0.05,
                        nrows = ifelse(num_plots_p > 4, 3, 2),
                        heights = if(num_plots_p > 4) {c(0.3,0.35,0.3)},
                        margin = c(0.05, 0.05, 0.05, 0.05))# |> 
                #layout(legend = list(x = 0, y = ifelse(num_plots_p>4, -0.05, -0.08),
                #       orientation = "h"))
  
  # Nutrient subplot
  subplots_n <- if(nutrient == TRUE & exists("plot_list_n")){
                  subplot(plot_list_n[names(plot_list_n) == site][1:num_plots_n],
                          titleY = TRUE, titleX = FALSE, #margin = 0.05,
                          nrows = ifelse(num_plots_n > 4, 3, 2),
                          margin = c(0.05, 0.05, 0.05, 0.05)) #|> 
                  # layout(legend = list(x = 0, y = ifelse(num_plots_n > 4, -0.05, -0.08),
                  #        orientation = "h"))
    }
    
##------------------------------------------------------------------------------
## Knit tabs                           
##------------------------------------------------------------------------------
  
  # Create unique chunk labels to use in the tab templates
  site_n <- paste0(site, '_n')
  site_p <- paste0(site, '_p')
  
  # Create tab chunk templates
  # Variables within {{}} are replaced by their value when the report is knit
  
  # if NOT reporting nutrients, use physical parameter template
    if(nutrient == FALSE) {
    template <- paste0(
      "## {{site_name}}{.tabset}\n", #create tab with site name
      #create chunk and set chunk options (height, width, echo)
      "```{r fig.height=", fig_height_p, ", fig.width=", fig_width, ", echo = FALSE}\n",
      "plot_title\n", #title of tab
      "\n",
      "fig_cap_p\n", #caption
      "subplots_p", #physical subplots
      "\n",
      "```\n",
      "\n",
     
      "```{r fig.height=0.18, fig.width = 9.2, echo = FALSE, dpi=300}\n",
      "legg",
      "\n",
      "```\n",
      
      "\n",
      "\n"
  )
    # if reporting nutrients, create physical and nutrient subtabs 
    } else {template <- paste0(
      "## {{site_name}}{.tabset}\n", #create tab with site name
      "### Field Measurements {.tabset}\n", #physical subtab
      
      "```{r fig.height=", fig_height_p, ", fig.width=", fig_width, ", echo = FALSE}\n",
      "plot_title\n", #title of tab
      "\n",
      "fig_cap_p\n", #caption
      "subplots_p", #physical subplots
      "\n",
      "```\n",
      "\n",
      
      "```{r fig.height=0.18, fig.width = 9.2, echo = FALSE, dpi=300}\n",
      "legg",
      "\n",
      "```\n",
      
      "\n",

      "### Lab Chemistry {.tabset}\n", #nutrient subtab
      
      "```{r fig.height=", fig_height_n, ", fig.width=", fig_width,", echo = FALSE}\n",
      "plot_title\n", #title of tab
      "\n",
      "fig_cap_n\n", #caption
      "subplots_n", #physical subplots
      "\n",
      "```\n",
      "\n",

      "```{r fig.height=0.18, fig.width = 9.2, echo = FALSE, dpi=300}\n",
      "legg",
      "\n",
      "```\n",
      
      "\n"
      
  )
}
  
  # Expand expressions within {{ }}
  tab <- knitr::knit_expand(text = template)
  
  # Knit results
  cat(knitr::knit(text = unlist(tab), quiet = TRUE))
  
}

```

## About the Sites
```{r leaflet, out.width="100%", message=F}
NPSbasic<-"https://atlas-stg.geoplatform.gov/styles/v1/atlas-user/ck58pyquo009v01p99xebegr9/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoiYXRsYXMtdXNlciIsImEiOiJjazFmdGx2bjQwMDAwMG5wZmYwbmJwbmE2In0.lWXK2UexpXuyVitesLdwUg"

NPSimagery="https://atlas-stg.geoplatform.gov/styles/v1/atlas-user/ck72fwp2642dv07o7tbqinvz4/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoiYXRsYXMtdXNlciIsImEiOiJjazFmdGx2bjQwMDAwMG5wZmYwbmJwbmE2In0.lWXK2UexpXuyVitesLdwUg"

NPSslate="https://atlas-stg.geoplatform.gov/styles/v1/atlas-user/ck5cpvc2e0avf01p9zaw4co8o/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoiYXRsYXMtdXNlciIsImEiOiJjazFmdGx2bjQwMDAwMG5wZmYwbmJwbmE2In0.lWXK2UexpXuyVitesLdwUg"

NPSlight="https://atlas-stg.geoplatform.gov/styles/v1/atlas-user/ck5cpia2u0auf01p9vbugvcpv/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoiYXRsYXMtdXNlciIsImEiOiJjazFmdGx2bjQwMDAwMG5wZmYwbmJwbmE2In0.lWXK2UexpXuyVitesLdwUg"

bbox <- read.csv("../boundboxes.csv") #lat/long coordinates and zoom level for each park 
site_csv <- read.csv(file = '../SiteInfo.csv') #site names, codes, and descriptions for popup 

# Find center coordinates of park box
long_cent <- mean(c(bbox$LongE[bbox$ParkCode == parkcode], bbox$LongW[bbox$ParkCode == parkcode]))
lat_cent <- mean(c(bbox$LatN[bbox$ParkCode == parkcode], bbox$LatS[bbox$ParkCode == parkcode]))

# Find the first and last date of monitoring for each site
years_active <- wdata_full |>  
 group_by(Site) |> 
 summarize(start_date = format(min(Date), "%b %Y"),
 last_date = format(max(Date), "%b %Y")) |> 
 ungroup()

# Compile water sites dataframe with codes, names, lat/long coordinates, and site type
water_sites1 <- data.frame(ParkCode = parkcode,       
                           Site = getSiteInfo(netnwd, parkcode = parkcode, info = "SiteCode"),
                           SiteName = getSiteInfo(netnwd, parkcode = parkcode, info = "SiteName"), 
                           lat = getSiteInfo(netnwd, parkcode = parkcode, info = "lat"),          
                           long = getSiteInfo(netnwd, parkcode = parkcode, info = "long"),
                           type = getSiteInfo(netnwd, parkcode = parkcode, info = "type")) 
water_sites2 <- left_join(water_sites1, years_active, by = c("Site"))
water_sites <- left_join(water_sites2, site_csv, by = c("Site" = "SiteCode", "ParkCode", "SiteName")) 
water_sites$Link = paste0("<a href='https://doimspp.sharepoint.com/sites/NETN_Photo_Viewer/Water_Quality_Site_Photos/", 
                     water_sites$Site, ".jpg' target='_blank'>Site Photo</a>")

# Legend html generator
# Source: https://stackoverflow.com/questions/47064921/leaflet-legend-for-addawesomemarkers-function-with-icons
# Icon library changed from font-awesome to ion

markerLegendHTML <- function(IconSet) {
    # Container div:
    legendHtml <- "<div style='padding: 10px; padding-bottom: 10px;'>
    <h4 style='padding-top:0; padding-bottom:10px; margin: 0; color:#555'> Legend </h4>" #legend title

    n <- 1
    # Add each icon for ion library icons:
    for (Icon in IconSet) {
        if (Icon[["library"]] == "ion") {
        legendHtml<- 
          paste0(legendHtml,
          # marker and marker label div
          "<div style='width: auto; height: 45px; display: flex; align-items: center;'>",
          # awesome marker div
          "<div style='position: relative; display: inline-block; width: 35px; height: 45px;' 
          class='awesome-marker-icon-", Icon[["markerColor"]]," awesome-marker'>",
          # add icons and set color
          # class='ion ion-waterdrop icon-white' selects the correct library, icon, and color
          "<i style='margin-left: 4px; margin-top: 11px' class= 'ion ion-",
            Icon[["icon"]]," icon-", Icon[["iconColor"]],"'></i>",
          "</div>", # close awesome marker div
          # legend label div - use name set in IconSet
          "<div style='position: relative; display: inline-block; margin-left: 8px;'>", 
            names(IconSet)[n] ,"</div>",
          "</div>") # close marker/marker label div    
        }
        n <- n + 1
    } 
    paste0(legendHtml, "</div>")
}

# Create list of icons to use in map
IconSet <- awesomeIconList(
  "Stream" = makeAwesomeIcon(icon= 'waterdrop', markerColor = 'blue', iconColor = 'white', library = "ion"),
  "Lake" = makeAwesomeIcon(icon= 'waterdrop', markerColor = 'cadetblue', iconColor = 'white', library = "ion")
)

# Create leaflet map
leaflet() %>%
    # set default view of park
    setView(lng = long_cent,
            lat = lat_cent,
            zoom = bbox$Zoom[bbox$ParkCode == parkcode]) %>%
    # setMaxBounds(lng1 = bbox[bbox$ParkCode == parkcode,]$LongE,
    #              lng2 = bbox[bbox$ParkCode == parkcode,]$LongW,
    #              lat1 = bbox[bbox$ParkCode == parkcode,]$LatN,
    #              lat2 = bbox[bbox$ParkCode == parkcode,]$LatS) %>%
    # add map tiles
    addTiles(group="Map", urlTemplate = NPSbasic, 
             options = providerTileOptions(minZoom = bbox$minZoom[bbox$ParkCode == parkcode])) %>%
    addTiles(group="Imagery", urlTemplate = NPSimagery) %>%
    addTiles(group="Light", urlTemplate = NPSlight) %>%
    addTiles(group="Slate", urlTemplate = NPSslate) %>%
    # add button to control map tiles
    addLayersControl(map = ., baseGroups = c("Map","Imagery","Light", "Slate"),
                     options = layersControlOptions(collapsed=T)) %>%
    # add site markers 
    addAwesomeMarkers(data = water_sites, ~long, ~lat, icon= ~IconSet[type], #style markers based on site type
                      # label on mouseover
                      label=as.character(water_sites$SiteName),
                      # popup on click
                      popup = paste0("<b>", water_sites$SiteName, "</b><br>",
                                     "<b>Type: </b>", water_sites$type, "<br>",
                                     "<b>Sample Period: </b>", water_sites$start_date, "&ndash;",
                                     water_sites$last_date, "<br>",
                                     water_sites$Description, "<br>",
                                     water_sites$Link
                                     )
                      ) %>%
    # add legend
    addControl(markerLegendHTML(IconSet = IconSet), position = "bottomleft")

```
```{r site_info, results = 'asis'}

# option 2: site descriptions below map
# for (i in site_list){
#   # split because the cat didn't work with multiple items
#   htmltools::h4(getSiteInfo(netnwd, park = parkcode, sitecode = i, info = "SiteName")) %>% 
#     as.character() %>% 
#     cat()
#   
#   site_info <- site_csv$Description[site_csv$SiteCode == i] 
#   htmltools::withTags(body(site_info)) %>% 
#     as.character() %>% 
#     cat()
# }

```

```{r About_tabs, child = "About_tabs.Rmd"}

```


